Column Comparison

### 2021-03-11 gc_column_comparison_2.Rmd
added new figure for bame standards

>>>>

```{r, fig.width=10, fig.height=6, warning=FALSE}
desired_points <- results$`Peak Name` %>% 
  str_subset(":0|18:")

p_bamesdb5zbfames <- results %>%
  filter(column_type %in% c("DB5", "ZBFAMES")) %>% 
  filter(standard_ID == "BAME") %>% 
  ggplot() +
    aes(x = `Retention Time`, y = `Relative Height`, fill = saturation, key = `Peak Name`, label = `Peak Name`) +
    geom_bar(stat = 'identity', width = 0.1) +
    facet_wrap(~column_type, ncol = 1) +
    ggtitle("BAME DB5/ZBFAMES") +
    # Subset labels
    geom_label_repel(data = . %>% 
                       mutate(label = ifelse(`Peak Name` %in% desired_points, `Peak Name`, "")),
                     aes(label = label),
                     show.legend = FALSE,
                     size = 2,
                     nudge_y = 2,
                     box.padding = .5,
                     label.r = 0) +
    coord_cartesian(ylim = c(0,11)) +
    theme_bw() +
    scale_fill_npg() +
    theme(legend.position = "bottom")
p_bamesdb5zbfames
